Stack Safety as a Security Property

### 2020-07-03 main.tex
a few comments on intro

\rb{Better section name and headings, references.}

\paragraph*{Micropolicies}
%
In order to enforce a given security policy on a system dynamically, we resort
to a programmable, tag-based reference monitor that runs alongside the program.
To control this monitor, we use a programming model that allows fine-grained
manipulation of metadata tags to encode so-called \emph{micropolicies}
\rb{cite}.

In such a system, all memory addresses, registers and the program counter are
enriched with an abstract metadata tag, which can point to the representation of
an arbitrary data structure. A micropolicy is thus defined by a collection of
rules to be checked as each instruction executes and together define the
transfer function of the security policy. Each rule inspects the tags associated
to the inputs of an instruction (PC, registers, memory) as well as the
instruction opcode itself, and produces one of two outcomes: either the
instruction is allowed to execute (and tags for the new PC and its result are
produced and assigned to those), or the machine fail-stops with a policy
violation.

Efficient execution of these micropolicies relies on hardware implementations
such as the PUMP architecture \rb{cite}, which include a monitor rule cache that
maps tag inputs to outputs and a mechanism to trap misses to software handlers
and thereby computes the transfer function of the software-defined policy.
Previous work has shown that a wide range of micropolicies can be defined and
enforced efficiently \rb{cite}.
%
\rb{Maybe go into more detail, examples later\ldots or try to segue into stack
policies}

>>>>

\paragraph*{Micropolicies}
